Vragenlijst thesis evaluatie

### 2015-08-15 doc/template/chap-4.tex
vanalles veranderd
verbetering stijn

The  spreading of malware has already been extensively researched. Because of the many different types of propagation methods it is hard to define a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph of the network in which the malware will spread itself. \\
Viruses and worms are the types of malware that are the most researched. Since the spreading of viruses requires human interaction, their propagation delay depends on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit this chapter to propagation models of worms. \\

The overview of this chapter will be as follows: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} illustrates a couple of models as examples to determine the propagation of a worm. These models can be used to extract parameter \textit{d}. Section \ref{eigenmatrixmethode} introduces an easy method to calculate the delay of the propagation of a worm. In the last section \ref{GoogleMatrix}, a method based on the PageRank algorithm of Google is used to determine which node has a higher probability of being infected by a worm. % Different kind of graphs to model a computer network are introduced.

@@

Infection by worms start by dropping the worm on the network. Different dropping mechanisms can be used, whereby the initial attack can be random or targeted at a specific node. Frequently used mechanisms are USB sticks (given to a specific person or left behind to be picked up by a random person), email, or malicious software through fishing or trojan horses. To determine the total delay, however, the propagation strategy is of higher importance than the drop mechanism. Propagation is achieved by determining the next nodes to spread the worm to. The following are common propagation methods: 
\begin{description}
%\item Scanning methods: A worm tries to guess (scan) the address of potential target nodes to infect. It can use distinct ways of scanning.
%% random, localized, topological or hit-list scanning.
%\begin{itemize}

@@

\item \textbf{Topology-based Worms} Email and other client application worms:An email worms uses the email systems to find email addresses to propagate. Other client applications can include: Internet Relay Chat (IRC), Instant Messenger (IM), and a variety of peer-to-peer
file sharing systems, which have been used by worms to propagate in a similar way as email worms. For example, the \textit{Kak worm} \citep{Kakworm} is a JavaScript computer worm that spread itself by exploiting a bug in Outlook Express. % Another example is `GhostNet'

>>>>

The spreading of malware has already been extensively researched. Because of the many different types of propagation methods it is hard to define a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph of the network in which the malware will spread. \\
Viruses and worms are the two most researched types of malware.
 Since the spreading of viruses requires human interaction, their propagation delay depends on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit this chapter to propagation models of worms. \\

The overview of this chapter will be as follows: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different models in section \ref{modelsforpropagation}. The models are used to extract parameter \textit{d}. Section \ref{eigenmatrixmethode} introduces an easy method to calculate the propagation delay of a worm. In the last section \ref{GoogleMatrix}, a method based on the PageRank algorithm of Google is used to determine which node has a higher probability of being infected by a worm. % Different kind of graphs to model a computer network are introduced.

@@

Infection by worms start by dropping the worm on the network. Different dropping mechanisms can be used, whereby the initial attack can be random or targeted at a specific node. Frequently used mechanisms are USB sticks (given to a specific person or left behind to be picked up by a random person), email, or malicious software through phishing or trojan horses. To determine the total delay, however, the propagation strategy is of higher importance than the drop mechanism. Propagation is achieved by determining the next nodes to spread the worm to. The following are common propagation methods: 
\begin{description}
%\item Scanning methods: A worm tries to guess (scan) the address of potential target nodes to infect. It can use distinct ways of scanning.
%% random, localized, topological or hit-list scanning.
%\begin{itemize}

@@

\item \textbf{Topology-based Worms:} Email and other client application worms: An email worms uses the email systems to find email addresses to propagate. Other client applications can include: Internet Relay Chat (IRC), Instant Messenger (IM), and a variety of peer-to-peer
file sharing systems, which have been used by worms to propagate in a similar way as email worms. For example, the \textit{Kak worm} \citep{Kakworm} is a JavaScript computer worm that spread itself by exploiting a bug in Outlook Express. % Another example is `GhostNet'
